Appendix

### 2023-09-24 manuscript/review/authorsResponse.qmd
changes in both reviewers.

---
title: Authors Response to Reviewer Comments
subtitle: "ECOSPHERE Manuscript ID (ECS23-0342) Tree regeneration in models of forest dynamics: a key priority for further research"

@@

date: last-modified
link-citations: true
linkcolor: blue
number-sections: true
format:
   pdf: 
     toc: true
---

@@

-

@@

Dear Charles,

Thank you very much for taking the time to review our manuscript and for your insightful thoughts on our findings.

We totally agree with your comments. Our main take away from this manuscript it is not that it would be impossible to calibrate all 15 models against e.g. the EuFoRIa data, but the issue is - as you wrote - that this needs to be bound to the goals of the study. And when the goal is to provide extrapolation into a future climate, then calibration against data under current climate may be unreliable. This is why we belive it is fundamentally valuable to test model performance "out of the box", as we have done here.

In this revised version we have modify the manuscript according to the reviewers' recommendations and we have addressed each of the specific points made in the review comments. We believe the manuscript has significantly improved based on this changes.

@@

@@

[I have to think about this again]{.underline}

Thank you for pointing

#### [COMMENT 2]{.underline}

The difference between 7 cm and 10 cm DBH in the observed data. From the methods, there is one dataset that has sites where recruitment was defined as 7 cm DBH, and then another where recruitment was somewhere between 7 -- 10 cm DBH. It was not clear how these were treated and compared in the results. I assume that the models simulated all 200 sites, but then the recruitment results were compared like-to-like. So, if a site defined recruitment as DBH = 8.0 cm, then all 15 models would compare simulated recruitment at that site only at 8 cm. Since the data are boxplots, I am not able to tell. For example, Figure 2 -- there should be 165 points for all of the 7 cm bars (observed and simulated) and 35 data points for the 10 cm bars (observed and simulated). If true, then please clarify. If not true, then please explain. Also, how was the data analysis performed when looking at the change in mortality and species diversity between 7 to 10 cm? I assume only the 165 stands were used. Please clarify. \

@@

Thank you for highlighting that we didn not managed to appropriately communicate our diameter thresholds approach correctly in the manuscript. The explanation is that the observed data

In this revised version we have revised the explanation in L XX

@@

[Based on the comments from Reviewer 1, we have re-analyse some of the results. More specifically we]{.underline}

@@

#### [COMMENT 4]{.underline}

@@

[check]{.underline}

#### [COMMENT 5]{.underline}

@@

[check]{.underline}

#### [COMMENT 6]{.underline}

@@

[change this]{.underline}

#### [COMMENT 7]{.underline}

@@

[check]{.underline}

#### [COMMENT 8]{.underline}

@@

@@

@@

@@

@@

@@

Figure 4 (and Figure S3) are interesting in that there are no patterns with overstory diversity, and that this was not explained by feedback with seed production. What happens if you colour the points, by those from models with the feedback? Do you address in the discussion why this feedback makes no difference to recruitment? \

@@

@@

@@

@@

#### COMMENT 17

@@

@@

@@

@@

@@

@@

@@

@@

@@

#### COMMENT 26

@@

@@

@@

#### COMMENT 1

@@

#### COMMENT 2 {#sec-R2C2}

@@

#### COMMENT 3

@@

@@

@@

[Following this and other comments from the editor, we have tried to capture this better in the discussion/conclussions section.]{.underline}

#### [COMMENT 15]{.underline}

@@

[ToDo find a reference!]{.underline}

@@

[ToDo find a reference!]{.underline}

#### [**COMMENT 18**]{.underline}

@@

We currently use the exciting Hanbury-brown 2022 review in several places across our manuscripts, following the reviewer's comment here and the general comment 2 in @sec-R2C2 we have also get inspired by their structure [by creating a road map to help the reader to navigate the manuscript content.]{.underline}

#### [**COMMENT 19**]{.underline}

@@

We believe the reviewer highlighted the words "models, such as deer browsing" because they think this is not correct. From our sample pool [only 4 models]{.underline} incorporated explicitly deer browsing.

@@

[**COMMENT 20**]{.underline}

@@

[We are unsure why the reviewer highlighted those words]{.underline}

@@

#### **COMMENT 25**

##### Response to comment 25: {#sec-R2C25r}

We agree with the reviewer's comment that there are other forest inventory data networks outside Central Europe even on forest reserves that could provide this sort of data. However, the EuFoRIa network is indeed novel and unprecedented network of forest reserves in Europe.

@@

Response to comment 33:

@@

L229 "Neither were further site information (except for the data specified below) nor any data " These were "blind trials":  modelling group were not provided with site information \...

@@

L230-231 "That is, the models were run in \"blind flight\" mode." Remove

@@

We understand the reviewers concern on not constraining the length of the simulations, but we decided to leave it to the assessment of the individual modelers, as we wanted to obtain simulation that were run from from bare ground in the absence of management to a simulated equilibrium (\"potential natural vegetation\") with current climate, and each modeler know best how to obtain this in each model. This information is currently available in the manuscript and in the protocol of this study.

@@

**COMMENT 44**

@@

@@

#### [**COMMENT 46**]{.underline}

@@

**COMMENT 47**

@@

Follwoing the reviewer recomendation we have changed the equation formulation to better represent the Reineke relationship. The reviewer is correct that the Reineke is applied to all stems in the stand, in our case the N value is only changing due to the available regeneration at the two diameter thresholds as the adult trees number is the same. By comparing our expected relationship of recruited trees at 7 and 10cm with the Reineke value we are just comparing to a theoretical value in fully stocked stands. We have use the coefficient -1.605 because Reineke attributed a general validity to this allometric coefficient for fully stocked, even-aged forest stands, regardless of tree species and site.

#### COMMENT 48

##### 
Response to comment 48:

The Stand Density Index by Reineke (1933) is based on the relationship between quadratic mean diameter and number of stems per unit area in fully stocked stands. We have use the coefficient -1.605 because Reineke attributed a general validity to this allometric coefficient for fully stocked, even-aged forest stands, regardless of tree species and site. This relationship was obtained by using pairs of variates for quadratic mean diameter and number of stems per unit area. In our study we are using the value of 1.77 to define this relationship between 7 and 10cm

@@

L316-317 "model complexity as defined by Bugmann and Seidl"

@@

[Think how can I add something else without making this much longer!]{.underline}

@@

COMMENT 52

@@

L530-533 "This substantial difference may be due to the fact that the simulation results were drawn from equilibrium forests, whereas in reality many of the forest reserves are recovering from past management activities and have become denser over the past decades (e.g., Heiri et al. 2009), leading to less regeneration than in an equilibrium situation. " But also \-\-- browsing, establishment sites,  competition with herb layer all reduce recruitment

@@

L596-598 "Competition for light as a strong filter for tree regeneration has been widely documented (Messier et al. 1999; Collet and Chenost 2006; Berdanier and Clark 2016), but the models examined here did not reproduce this expectation. ", because \... remind us of the evidence you are putting forward

@@

#### 
[COMMENT 58]{.underline}

L676-677 "Therefore, we further recommend that more effort should be invested into collecting harmonized datasets on tree regeneration." regeneration in what sense?   Seedlings/ ground layer/ \....  What is really needed?

@@

Following the reviewers comment we have included this text:

@@

[COMMENT 59]{.underline}

L685-687 However, this will require an entirely different set of observed data, and potentially not all models of forest dynamics would be able to assess the relationship of these aspects on tree regeneration, e.g. due to the lack of disturbance or appropriate management modules.

##### 
Response to comment 59:

Following the reviewers comment we have included this text:

[COMMENT 60]{.underline}

L696 "Exercises like the one presented here, where the models are operated in \"blind flight\" mode." Definition of blind flight "To do something based on guesswork, intuition, or without any help or instructions"\....is that what you mean?

Response to comment 60:

Following the reviewers comment we have included this text:

>>>>

---
title: Authors Response to Reviewer's Comments
subtitle: "ECOSPHERE Manuscript ID (ECS23-0342) Tree regeneration in models of forest dynamics: a key priority for further research"

@@

date: last-modified
link-citations: true
linkcolor: blue
number-sections: true
format: docx
---

@@

@@

Dear Dr. Charles Canham,

I want to express my gratitude for taking the time to review our manuscript. Your insightful thoughts on our findings were very helpful.

Our main takeaway from this manuscript is that while it may be possible to calibrate all 15 models against the EuFoRIa data, it is important to ensure that this aligns with the study's goals. If the goal is to provide extrapolation into a future climate, calibrating against data under the current climate may not be reliable. This is why we believe it is valuable to test model performance without any changes or calibration as we have done in this study.

We have carefully reviewed and addressed each of the specific points made in the review comments in this revised version. We believe that the changes we made have significantly improved the manuscript. Once again, I want to thank you for the time and effort you dedicated to reviewing our work. We look forward to hearing from you again.

Best regards,

Olalla Díaz-Yáñez on behalf of all the co-authors

@@

Dear Reviewer 1,

Thank you for taking the time to review our manuscript. We appreciate your thoughtful comments and have carefully considered each of them. We have made changes to the manuscript based on your feedback and believe that these changes have improved the overall quality of the work.

We understand your concern about the length of the manuscript and the number of figures included. We have made an effort to reduce the text where possible and have verified that we are following the journal guidelines. Despite our best efforts, however, it has been difficult to significantly reduce the length of the manuscript.

Please find below our responses to each of your comments and the concrete actions we have taken in response.

Thank you again for your valuable feedback.

@@

[We should discuss this point again... I do not agree to simple change regeneration with recruitment. Specially without a detailed definition as we had in the previous version.]{.underline}

[SUGGESTION FROM YANNEK:]{.underline}

[Thank you for pointing this out. We also discussed terminology several times and we agree. We followed your suggestion replaced 'regeneration' with 'recruitment' where the difference is not clear. However, we believe that in some places regeneration is more accurate. Especially in many parts of the introduction and discussion. We argue that regeneration is often only modeled via "recruitment", but with the aim to simulate the whole process of regeneration. In this context it makes more sense to use the general term (e.g., for discussion consequences.)]{.underline}

[COMMENT from YK: I would argue that recruitment is evidence for successful regeneration. This allows us to use recruitment for discussions observation vs. simulation in both aspects: technical (recruitment) and general (regeneration).]{.underline}

#### COMMENT 2

The difference between 7 cm and 10 cm DBH in the observed data. From the methods, there is one dataset that has sites where recruitment was defined as 7 cm DBH, and then another where recruitment was somewhere between 7 -- 10 cm DBH. It was not clear how these were treated and compared in the results. I assume that the models simulated all 200 sites, but then the recruitment results were compared like-to-like. So, if a site defined recruitment as DBH = 8.0 cm, then all 15 models would compare simulated recruitment at that site only at 8 cm. Since the data are boxplots, I am not able to tell. For example, Figure 2 -- there should be 165 points for all of the 7 cm bars (observed and simulated) and 35 data points for the 10 cm bars (observed and simulated). If true, then please clarify. If not true, then please explain. Also, how was the data analysis performed when looking at the change in mortality and species diversity between 7 to 10 cm? I assume only the 165 stands were used. Please clarify.

@@

Thank you for bringing to our attention the issue with the way we communicated our diameter thresholds approach in the manuscript. The observed data had varying diameter thresholds for reporting tree recruitment, and, for the purposes of this study, we merged the recruited trees values into two thresholds of 7 and 10cm.

In total, we had 165 sites where the records showed the number of recruited trees at a 7cm threshold. For these sites, any recruited tree above 7cm was counted. We also had 35 sites where the minimum diameter threshold was 10cm, and for these sites, we could only account for trees recruited from 10cm diameter. We used the other 165 sites with 7cm diameter threshold in the 10cm database, but only accounting for newly established trees above 10cm. There was no like-to-like comparison for any other diameter threshold, only for 7 and 10cm.

The reviewer correctly pointed out that in Figure 2 for the 7cm threshold, there were 165 "dots" in the observed data, while for the 10cm diameter threshold, there were 200 "dots." However, simulated values were obtained for the 200 sites for both thresholds, as explained in the Simulation protocol section. Therefore, the simulated values in the figures are from the 200 sites.

When examining the change in mortality between 7 to 10cm or species diversity comparison between observed and simulated data (Figure 4), we could only use the 165 sites that contained both pieces of information at the 7 and 10cm thresholds in the observed data. This is reported in the supplementary materials software, script \`\`\`Figures.R\`\`\` line 536 and L284-349 and now better explained in the manuscript.

To better clarify this aspect, we have made the following changes:

1\) We have better explained the difference on the observed data in the section 3.2 Observed data with the following text:

"For our study, we defined two datasets where one included 165 sites with a diameter threshold of 7 cm or lower, and the other included another 35 sites with diameter thresholds from 10 cm. Therefore we had in total 200 sites with observations of newly established trees above 10 cm and 165 sites above 7cm. In the results section any result from observed data at 7 cm threshold is originated from the 165 sites."

2\) We have added the following text in the caption of figure 4

"B) Examples for the three trends across models for regeneration at the 7 cm threshold (165 sites)."

@@

[I am going to do this.]{.underline}

@@

@@

We have made some changes to the abstract based on feedback from both reviewers, including clarifying certain parts for better understanding. The models were able to capture some aspects of regeneration more effectively than others. One example, is the sentence highlighted by the reviewer that was refereing to the diversity of regeneration.

@@

Following the reviewers comments we have made several changes in this paragraph to improve its readability and flow if ideas with the main purpose of the study text.

@@

Following the reviewers comment we have added a new column classifying the models in recruit or regeneration models; and the letters a,b,c, d,e and f table are now better described. Regarding the suggestion on adding into this table the size of the saplings or ingrowth: there are models that start from saplings or ingrowth what without a constant diameter threshold as they are biomass based (e.g. LandClim), we find it complicated to add all this information in this table without making it too large and therefore we have decided not to included. Furthermore the models reports in the supplementary materials provide more details on how the models simulate regeneration.

ToDo All models check that the new column in the table is correct for your model.

@@

Yes, this is the mean value across all observations and sites, there are two main reasons why this number might seem low, first due to the zero inflated nature of the data, and second because these are forest reserves, corresponding with denser forests in which regeneration would be expected to be lower. This value is in agreement with a further observed data from reserved (Käber, Y., et al (2023). Sheltered or suppressed? Tree regeneration in unmanaged European forests. Journal of Ecology, 00, 1--15. https://doi.org/10.1111/1365-2745.14181)

@@

For those models that simulated more than the eleven species, we created a different category "others" were we lumped those extra recruited species. This were counted when we calculated the diversity index and for total recruitment values. Following the reviewer comments we have added this information in the simulation protocol section with the following text:

"Two models included their standard set of species for the simulations, which is much larger (i.e., ForClim 1, ForClim 11, TreeMig), the species simulated beyond the eleven species were lumped in a category "others""

#### COMMENT 9

@@

Following the reviewers comment we have modified this text to improve it readability with:

"Furthermore, regarding the share in the regeneration basal area per species ($\bar{R}_{BA_{share_{i}}}$), we categorized this as zero when the regeneration basal area of that species ($\bar{r}_{BA_{t,i}}$) was zero, but also when both the total regeneration basal area ( $\sum_{i = 1}^{s}{\bar{r}_{BA_{t,i}}}$) and the regeneration basal area of that species ($\bar{r}_{BA_{t,i}}$) equaled zero."

@@

Even thought it is not directly comparable, we still believe is interesting for the reader that we share the findings related to the 4C model and those that simulate more species that were lumped in the category others.

#### [COMMENT 11]{.underline}

@@

[To be addressed in combination with COMMENT 3]{.underline}

@@

Following the reviewers comment we have increased the legend size, and now the difference between observed and simulated is visible. We have also explained in the caption the meaning of the black line:

"Mean Shannon index per site at recruitment and at the stand level both for observed and simulated values for the diameter threshold of 7cm. The black line marks where the mean Shannon index per site at recruitment and at the stand level would be equal"

@@

Figure 4 (and Figure S3) are interesting in that there are no patterns with overstory diversity, and that this was not explained by feedback with seed production. What happens if you colour the points, by those from models with the feedback? Do you address in the discussion why this feedback makes no difference to recruitment?

@@

We agree with the reviewer that it was interesting to find that the models with feedback did not captured better the species diversity of the regeneration compared with those without, with the exeption of ForCEEPS. The Figure 4 shows three representative patterns observed across models using 6 of them as an example, and the Figure S3 provides the details for each model. Models with feedback are defined in table 1 and are ForCEEPS(f) , PICUS, SIBYLA, xComp, iLand, LandClim, Landis-II, TreeMig, LPJ-GUESS, and aDGVM2. We have addressed this point in the discussion section with the following text:

"Furthermore, based on the simulation results, there is no evidence that models with feedback from the canopy (in terms of species composition of regeneration) captured better the species diversity of the regeneration than those without feedback, with the exception of ForCEEPS that significantly improved regeneration species diversity with the model version that included feedback (ForCEEPS(f)). The similar performance of models with and without feedback is likely because the models put more weight on the regeneration niche arising from abiotic and biotic filters, than from the habitat niche of the adult trees [@grubb1977]."

@@

Following the reviewers recommendation we have changed the axis labels in the appendix figures.

@@

This paragraph is addressing the comparison with the theoretical Reineke value which is usually calculated for even-aged, single species stands and assumes a fixed relationship between the number of stems and the quadratic mean diameter in fully stocked pure stands.

@@

Thank you! We also think is a good summary figure.

@@

[Clean together with comment 2]{.underline}

@@

Following the reviewer comment we have removed figure S7.

@@

Figure 4 shows three examples of the patterns observed across models (overestimation intermediate and underestimation) using one exemplary model of each category , the actual patterns per model can be found in Figure S3. In the results we showed that most models captured reasonably well or overpredicted species diversity at the stand level, as most of the models are under the patterns presented in plot 1 and 2 from A on Figure 4. We have decided to keep the referenced statement link to this findings in the discussion as it was.

@@

In this statement we were referring only to regeneration levels. Although we agree with the reviewer that we did state that most of the models overestimate regeneration, here our point is that even-thought they did overestimate regeneration they did not deviate exceedingly, specially under the consideration that these models have never been confronted with this type of data.

@@

With this statement we were referring to the multiple potential combinations of approaches of modeling tree regeneration. Based on the reviewers comment we have modified this for clarity.

@@

Thank you for noticing this. We have now corrected this mistake.

@@

We agree with the reviewer that ideally models should be able to capture broader patterns. With this sentence we just wan to explain that the stochasticity of this process may have partly explained the results on this regard.

@@

The reviewer is correct that landscape level models were not significantly performing worst than others. Here we just wanted to discuss that maybe another spatial consideration will have allowed landscape level models to better represent regeneration processes as they are designed for that.

@@

We agree with the reviewer, a coarse representation of water balance would not make it more sensitive to water deficits. And this was exactly our point in this part of the discussion where we wrote: "This may at least partially explain the unsatisfactory performance of many models along the drought axis (i.e., climatic water balance)."

#### [COMMENT 26]{.underline}

@@

Following the reviewers comment we have expanded this aspect in the following paragraph XXXX

[Both reviewers asked to be more specific on the data we are missing, what vairables would you say without being too detailed? also linked to comment 59 from reviewer 2]{.underline}

@@

Dear Reviewer 2,

We would like to express our sincere gratitude for all the detailed comments they provided on our manuscript. We have carefully considered all of their feedback and made the necessary changes to improve the manuscript. Thanks to your comments, we have improved our manuscript.

Thank you again for your valuable feedback.

@@

@@

[I think we have proposed some ideas of how to do this better in the discussion. What else do you think we should add here?]{.underline}

#### [COMMENT 2]{.underline} {#sec-R2C2}

@@

Following the reviewer comment we have added a "road map" at the end of the introduction.

@@

[Decide final terminology]{.underline}

@@

The reviewer is correct that most of the people involved in this manuscript have a central European focus in their current work, and so did the study set up. We have included some relevant global or with a focus outside Europe references when relevant. e would be happy to consider some other relevant suggestions.

@@

[Following this and other comments from the editor, we have tried to capture this better in the discussion/conclussions section. Should we add something on this?]{.underline}

@@

[ToDo find a reference! Any suggestions?]{.underline}

@@

[ToDo find a reference!Any suggestions?]{.underline}

#### **COMMENT 18**

@@

We currently use the exciting Hanbury-brown 2022 review in several places across our manuscripts, following the reviewer's comment here and the general comment 2 in @sec-R2C2 we have also get inspired by their structure by creating a road map to help the reader to navigate the manuscript content.

#### **COMMENT 19**

@@

We believe the reviewer highlighted the words "models, such as deer browsing" because they think this is not correct. From our sample pool only 4 models incorporated explicitly deer browsing.

@@

#### **COMMENT 20**

@@

We are unsure why the reviewer highlighted those words

@@

@@

##### Response to comment 33:

@@

L229 "Neither were further site information (except for the data specified below) nor any data" These were "blind trials":  modelling group were not provided with site information \...

@@

L230-231 "That is, the models were run in "blind flight" mode." Remove

@@

We understand the reviewers concern on not constraining the length of the simulations, but we decided to leave it to the assessment of the individual modelers, as we wanted to obtain simulation that were run from from bare ground in the absence of management to a simulated equilibrium ("potential natural vegetation") with current climate, and each modeler know best how to obtain this in each model. This information is currently available in the manuscript and in the protocol of this study.

@@

#### **COMMENT 44**

@@

L1046 Such converting to effective no of species using Jost formula

@@

#### **COMMENT 46**

@@

#### COMMENT 47

@@

Following the reviewer recomendation we have changed the equation formulation to better represent the Reineke relationship. The reviewer is correct that the Reineke is applied to all stems in the stand, in our case the N value is only changing due to the available regeneration at the two diameter thresholds as the adult trees number is the same. By comparing our expected relationship of recruited trees at 7 and 10cm with the Reineke value we are just comparing to a theoretical value in fully stocked stands. We have use the coefficient -1.605 because Reineke attributed a general validity to this allometric coefficient for fully stocked, even-aged forest stands, regardless of tree species and site.

@@

L316-317 "model complexity as defined by Bugmann and Seidl" say a little more...

@@

[Any suggestion of how can I add something else without making this much longer!]{.underline}

@@

#### COMMENT 52

@@

L530-533 "This substantial difference may be due to the fact that the simulation results were drawn from equilibrium forests, whereas in reality many of the forest reserves are recovering from past management activities and have become denser over the past decades (e.g., Heiri et al. 2009), leading to less regeneration than in an equilibrium situation." But also \-\-- browsing, establishment sites,  competition with herb layer all reduce recruitment

@@

L596-598 "Competition for light as a strong filter for tree regeneration has been widely documented (Messier et al. 1999; Collet and Chenost 2006; Berdanier and Clark 2016), but the models examined here did not reproduce this expectation.", because \... remind us of the evidence you are putting forward

@@

#### COMMENT 58

L656 "Yet, the global models should not be at a disadvantage due to the limited spatial consideration" Don't quite follow your point here. what does "at a disadvantage" mean?

@@

In this sentence we are discussing how the sampling strategy presented in the study protocol might have represented a disadvantage for landscape level models due to the limited spatial scale, but how this might not be the same for Global level models as they usually lack dispersal between cells.

#### [COMMENT 59]{.underline}

L676-677 "Therefore, we further recommend that more effort should be invested into collecting harmonized datasets on tree regeneration." regeneration in what sense?   Seedlings/ ground layer/ ....  What is really needed?

[Linked to comment 26 from reviewer 1]{.underline}

#### COMMENT 60

L685-687 "However, this will require an entirely different set of observed data, and potentially not all models of forest dynamics would be able to assess the relationship of these aspects on tree regeneration, e.g. due to the lack of disturbance or appropriate management modules." more akin to data already available in national inventories I think

##### Response to comment 60:

We agree with the reviewer that a more systematic kind of inventory could be useful to detect regeneration patterns under management or disturbances impacts.

@@

#### COMMENT 61

L696 "Exercises like the one presented here, where the models are operated in "blind flight" mode." Definition of blind flight "To do something based on guesswork, intuition, or without any help or instructions"....is that what you mean?

##### Response to comment 60:

With blind flight we refer to doing the simulations without having important information about the expected regeneration values.

#### COMMENT 62

Table 1 caption: A useful table. I'd encourage the authors to write a lengthier table heading, which briefly summarises the methods section, so that readers can know what "start from", "runtime for sampling" mean without having to delve into the text. Also I'd like to see an explanation of "formulation complexity" in the text and here. The supplementary information gives more details about model assumptions, and I do wonder whether those could be included here; in particular, seed production and dispersal is clearly important for regeneration, so could columns be introduced to compare assumptions of model with respect to these. Also deer browsing, herb-layers and nurse logs all have an influence of regeneration, but not incorporated into these models; I suggest the table heading makes that clear.

##### Response to comment 62:

Following the reviewers comment we have expanded the caption of table 1 with the following text:

"Models included, their characteristics and simulation strategies used in this study. Where Scale refers to the models scale, *Type* to the models type, *Population structure* to the model population approach, *Feedback* to the inclusion or not of adult tree feedback to the level and species composition of regeneration, *Approach* to the model regeneration module approach, *Start from* to the stage from which trees are recruited, *Complexity,* to *the* mean regeneration formulation as estimated in (Bugmann & Seidl, 2022), *Species* to which species from the original eleven species were simulated , *Runtime (spin up) \[years\]* to the number of years used per model in their simulations for the spin up period and regeneration sampling; *Climate data type (use of years)* to the type of data used in the simulations and how it was used, and Reference provides the link to the publication with more model details. Further information can be found on the individual model reports available in the supplementary materials."

#### COMMENT 63

L831 Add publisher

L939 Correct doi

##### Response to comment 63:

#### 
[COMMENT 64]{.underline}

L1041 suggest sticking with "ingrowth" (as used in the figure) or "recruitment"

##### Response to comment 65:

[To follow up after terminology discussion]{.underline}

#### COMMENT 65

L1050 Overperdicted

##### Response to comment 65:

#### 
COMMENT 66

L1056 no mortality of recruits as they grow from 7 to 10 cm diameter.

##### Response to comment 66:

We use the difference of observed trees recruited between 7 and 10cm as a proxy for mortality.

#### 
COMMENT 67

L1077 Explain the fitted curves

##### Response to comment 67:

We are not sure if we are correctly understanding the reviewers point here. In figure 8 we do not show any fitted curves.

### 2023-09-24 manuscript/supplementaryRW.Rmd
changes in both reviewers.

```{r recrStand7, echo=FALSE, fig.cap="Mean Shannon index per site at recruitment and at the stand level both for observed and simulated values for the diameter threshold of 7cm", out.width='100%', fig.pos='H'}
knitr::include_graphics(here::here("figures", "recruitmentAdultRichness7.png"))
```

@@

```{r nvTrend710, echo=FALSE, fig.cap="Mean ingrowth values across the 200 samples per site, for the 200 sites against gradients of (a) total basal area; (b) climatic water balance; (c) seasonal degree sum. The values were split into ten bins; the red lines represent a GAM model showing the trend in the observed data.", fig.show = 'hold', out.width="49%",fig.ncol = 2, fig.subcap=c('', '', ''), fig.show='hold', fig.align='left'}
   knitr::include_graphics(c(here::here("figures", "envTrend7Totba_500.png"),
                              here::here("figures", "envTrend7WB_500.png"),
                              here::here("figures", "envTrend7DDS_500.png")))
```

>>>>

```{r recrStand7, echo=FALSE, fig.cap="Mean Shannon index per site at recruitment and at the stand level both for observed and simulated values for the diameter threshold of 7cm. The black line marks where the mean Shannon index per site at recruitment and at the stand level would be equal", out.width='100%', fig.pos='H'}
knitr::include_graphics(here::here("figures", "recruitmentAdultRichness7.png"))
```

@@
